A systematic search for transiting planets in the \KT\ data

### 2015-05-01 ms.tex
comments from scholkopf

% Notation for this paper.
\newcommand{\flux}{{\ensuremath{f}}}
\newcommand{\ferr}{{\ensuremath{\sigma_\flux}}}
\newcommand{\attime}{{\ensuremath{t}}}
\newcommand{\basis}{{\bvec{A}}}
\newcommand{\weights}{{\bvec{w}}}

@@

\newcommand{\nyu}{2}
\newcommand{\caltech}{3}
\newcommand{\cfa}{4}
\newcommand{\mpia}{5}
\newcommand{\cds}{6}
\newcommand{\princeton}{7}
\newcommand{\mpis}{8}
\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\nyu},
    Benjamin~T.~Montet\altaffilmark{\caltech,\cfa},
    David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
    Timothy~D.~Morton\altaffilmark{\princeton},
    Dun~Wang\altaffilmark{\nyu}, \&
    Bernhard~Sch\"olkopf\altaffilmark{\mpis}
}
\altaffiltext{1}         {To whom correspondence should be addressed:
                          \url{danfm@nyu.edu}}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          Department of Physics, New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\caltech}  {Cahill Center for Astronomy and Astrophysics,
                          California Institute of Technology, Pasadena, CA,
                          91125, USA}
\altaffiltext{\cfa}      {Harvard-Smithsonian Center for Astrophysics,
                          Cambridge, MA 02138, USA}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\cds}      {Center for Data Science,
                          New York University,
                          726 Broadway, 7th Floor, New York, NY, 10003, USA}
\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
                          Princeton, NJ, 08544, USA}
\altaffiltext{\mpis}     {Max Planck Institute for Intelligent Systems
                          Spemannstrasse 38, 72076 T\"ubingen, Germany}

@@

One key realization that is also exploited by the official \kepler\ pipeline
is that the systematic trends caused by pointing shifts and other instrumental
effects are shared---with different signs and weights---by all the stars on
the focal plane.
To capitalize on this, the \pdc\ component of the \kepler\ pipeline
removes any trends from the light curves that can be fit using a linear
combination of a small number of ``co-trending basis vectors''.
This basis of trends was found by running Principal Component Analysis (PCA)
on a large set of (filtered) light curves and extracting the top few ($\sim
4$) components \citep{Stumpe:2012, Smith:2012}.
Similarly, we ran PCA on the full set of our own generated \KT\ Campaign~1
light curves to determine a basis of representative trends but, unlike \pdc,
we retain and use a larger number of these components ($150$).
For clarity, we will refer to our basis as a set of ``eigen light curves''
(ELCs) and the full set is made available online\footnote{\datareleaseurl}.
The top ten ELCs for Campaign~1 are shown in \Fig{pca}.

@@

Physically, the motivation for our model---and the \pdc\ model---is that every
star on the detector should be affected by the same set of systematic effects.
These are caused by things like pointing jitter, temperature variations, and
other sources of PSF modulation.
Each of these effects will be imprinted in the light curves of many stars with
varying amplitudes and signs as a result of the varying flat field and PSF.
Therefore, while it is hard to write down a physical generative model for the
systematics, building a data-driven model might be possible.
This intuition is also exploited by other methods that model the systematics
using only empirical centroids \citep{Vanderburg:2014, Armstrong:2014,
Aigrain:2015, Crossfield:2015}, but our more flexible model should capture a
wider range of effects, including those related to PSF and temperature.
For example, \Fig{corr} shows the application of our model---with 150
ELCs---to a light curve with no known transit signals and the precision is
excellent.

@@

In our pipeline we simultaneously fit for the transit signal and the trends
using a rigid model for the signal and a relatively flexible model for the
systematic noise.
Specifically, we model the light curve as being generated by linear
combination of 150 ELCs and a ``box'' transit model at a specific period,
phase, and duration.
The mathematical details are given in \app{math}, but in summary, since the
model is linear, we can analytically compute the likelihood
function---conditioned on a specific period, phase, and duration---for the
depth \emph{marginalizing out the systematics model}.
The signal-to-noise of this depth measurement can then be used as a quality of
fit metric or candidate selection scalar.
This computation is expensive but, as described in the following \sectionname
s, it is possible to scale the method to a \KT-size dataset.
\response{The bottom panel of \Fig{overfitting} shows the application of this
joint transit--systematics model to the synthetic transit discussed
previously.
When the joint model is used, the correct transit depth is measured---the
transit is not distorted---but the systematics are also well-described by the
model.}

@@

\begin{figure}[p]
\begin{center}
\includegraphics{figures/corr.pdf}
\end{center}
\caption{%
A demonstration of the ELC fit to the aperture photometry for EPIC 201374602.
\emph{Top:} The black points show the aperture photometry and the green line
is the maximum likelihood linear combination of ELCs.
The estimated 6-hour precision of the raw photometry is 264 ppm.
\emph{Bottom:} The points show the residuals of the data away from the ELC
prediction.
The 6-hour precision of this light curve is 31 ppm.
Note that although we show a ``de-trended'' light curve to give a qualitative
understanding of the model, this is not a product of the analysis.
In this search for transits, \emph{the data are never de-trended}.
\figlabel{corr}}
\end{figure}

\begin{figure}[p]
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/overfitting.pdf}
\end{center}
\caption{%
\response{%
A comparison between de-trending using different numbers of ELCs and a
simultaneous fit of the systematics and transit model.
\emph{(a)} The raw photometry for EPIC 201374602 with a synthetic transit
injected at 65 days. In all plots, the photometry is measured in
parts-per-thousand (ppt).
\emph{(b)} The black points show the photometry de-trended using a linear
combination of 10 ELCs and the green line shows the true transit model.
The maximum likelihood transit depth is computed following \project{BLS}
\citep{Kovacs:2002}.
While some of the systematics are removed by this model, there is still a lot
of residual noise.
\emph{(c)} The same plot as panel \emph{(b)} but using 150 ELCs to de-trend.
This model removes the majority of the systematics but also distorts the
transit and weakens the signal; it reduces the measured transit depth.
\emph{(d)} The final panel shows the results of simultaneously fitting for
the transit and the systematics using 150 ELCs.
The maximum likelihood depth is computed as described in \app{math}.
Like panel \emph{(c)}, this model removes most of the systematics but does
not distort the transit or reduce the measured transit depth.
}
\figlabel{overfitting}}
\end{figure}

@@

Specifically, we must evaluate the likelihood function for the light curve of
star $n$ given a period \period, reference transit time \phase, duration
\duration, \response{and depth \depth}
\begin{eqnarray}\eqlabel{full-likelihood}
p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration,\,\depth) \quad.
\end{eqnarray}
We make the simplifying assumption that each transit enters this quantity
independently.
This is not true; as we change beliefs about each transit, we change beliefs
about the systematics model, which in turn affects the other transits.
However, this simplifying assumption
is approximately satisfied for all but the shortest
periods and leads to a huge computational advantage.
Under this assumption, this likelihood function can be rewritten as
\begin{eqnarray}\eqlabel{indtran}
p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration,\,\depth) &=&
\prod_{m=1}^{M(\period,\,\phase)}
    p(\{\flux\}_n\,|\,\transittime_m(\period,\,\phase),\,\duration,\,
                    \depth)
\end{eqnarray}
where $\transittime_m(\period,\,\phase)$ is the time of the $m$-th
transit given the period $\period$ and reference time $\phase$, and
\response{$M(\period,\,\phase)$ is the total number of transits in the dataset
for the given \period\ and \phase}.
\Eq{indtran} can be efficiently computed for many periods and phases if we
first compute a set of likelihood functions for single transits on a grid
in $\transittime_l$ and duration $\duration_k$
\begin{eqnarray}\eqlabel{singletransit}
\left \{ p(\{\flux\}_n\,|\,\transittime_l,\,\duration_k,\,\depth)
\right\}_{l=1,\,k=1}^{L,\,K} \quad.
\end{eqnarray}
Then, we can use these results as a look-up table\response{---with
nearest-neighbor interpolation---}to approximately evaluate the full
likelihood in \eq{full-likelihood}.

@@

The linear search requires hypothesizing a set of transit signals on a
two-dimensional grid in transit time and duration.
For each point in the grid, we use the model described in \sect{model} to
evaluate \emph{the likelihood function} for the transit depth at that time
and duration.
Since the model is linear, the likelihood function for the depth (marginalized
over the model of the systematics) is a Gaussian with analytic amplitude $L$,
mean $\bar{\depth}$, and variance $\delta\bar{\depth}^2$, all derived and given in
\app{math}.
In the linear search, we save these three numbers on a
two-dimensional grid of transit times $\transittime_l$ and durations
$\duration_k$.
The transit time grid spans the full length of Campaign~1 with half hour spacing
and we choose to only test three durations: 1.2, 2.4, and 4.8 hours.
\Fig{linear} shows the maximum likelihood transit depth $\bar{\depth}$ as a
function of transit time \transittime\ for the light curve of EPIC 201613023,
a transiting planet candidate with a period of 8.3~days.

@@

\response{%
In the period search step, the table of likelihood functions generated in the
linear search step are used to compute the likelihood of the periodic model
(\eqalt{indtran}) on a three dimensional grid in period \period, reference
time \phase, and duration \duration.
At each point in this grid, the likelihood function for each transit depth is
chosen as the nearest point calculated in the linear search.
If the time spacing of the linear search is sufficiently fine, this will give
a good approximation of the correct periodic likelihood.}
For each periodic model, we compute the likelihood of a model where the
transit depth varies between transits and the ``correct'' simpler model where
the transit depth is constant.
The variable depth likelihood is given by the product of amplitudes from the
initial search
\begin{eqnarray}
p_\mathrm{var}(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) &=&
\prod_{m=1}^{M(\period,\,\phase)} L_m \quad.
\end{eqnarray}
Since the likelihood function for the depth at each transit time is known and
Gaussian, the likelihood function for the depth under the periodic model can
also be computed analytically; it is a product of Gaussians which itself is a
Gaussian
\begin{eqnarray}
p_\mathrm{const}(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) &=&
\prod_{m=1}^{M(\period,\,\phase)}
    \frac{L_m}{\sqrt{2\,\pi\,{\delta\bar{\depth}_m}^2}}\,\exp \left(
        -\frac{[\depth - \bar{\depth}_m]^2}{2\,{\delta\bar{\depth}_m}^2}
    \right)
\end{eqnarray}
where the maximum likelihood depth, for the periodic model, is
\begin{eqnarray}\eqlabel{periodic-depth}
\depth &=& {\sigma_\depth}^2\,\sum_{m=1}^{M(\period,\,\phase)}
    \frac{\bar{\depth}_m}{{\delta\bar{\depth}_m}^2}
\end{eqnarray}
and the uncertainty is given by
\begin{eqnarray}\eqlabel{periodic-depth-uncert}
\frac{1}{{\sigma_\depth}^2} &=& \sum_{m=1}^{M(\period,\,\phase)}
    \frac{1}{{\delta\bar{\depth}_m}^2} \quad.
\end{eqnarray}
Note that this result has been \emph{marginalized} over the parameters of the
systematics model.
Therefore, this estimate of the uncertainty on the depth takes any
uncertainty that we have about the systematics into account.

In general, the variable depth model will \emph{always} get a higher
likelihood because it is more flexible.
Therefore, a formal model comparison is required to compete these two models
against each other on equal footing.
For computational simplicity and speed, we use the Bayesian Information
Criterion (BIC).
The traditional definition of the BIC is
\begin{eqnarray}
-\frac{1}{2}\,\BIC &=&
    \ln p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration)
    - \frac{K}{2} \ln N
\end{eqnarray}
where the likelihood function is evaluated at the maximum, $K$ is an estimate
of the model complexity and $N$ is the effective sample size.
To emphasize that $K$ and $N$ are tuning parameters of the method, we
rewrite this equation as
\begin{eqnarray}
-\frac{1}{2}\,\BIC &=&
    \ln p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) -
        \frac{J\,\alpha}{2}
\end{eqnarray}
where $J$ is the number of allowed depths---one for the constant depth model
and the number of transits for the variable depth model---and $\alpha$ is
chosen heuristically.
For the K2 Campaign~1 dataset, we find that $\alpha \sim 1240$ leads to
reliable recovery of injected signals while still being fairly insensitive to
false signals.

@@

To do first-pass vetting for blended EBs among our catalog of
planetary candidates, we test for significant centroid offsets using
the machinery that we have already established for modeling the
systematic trends in the data, inspired by the methods used to vet
\kepler\ candidates \citep{Bryson:2013}.  This is only an initial vetting step
and a more complete characterization of our catalog's reliability is
forthcoming (Montet, \etal\ in preparation).

@@

To test the performance and detection efficiency of our method, we conducted a
suite of injection and recovery tests, five per
star for all 21,703 target stars.
For each test, we inject the signal from a realistic planetary system into the
raw aperture photometry of a random target and run the resulting injected
light curve through the full pipeline (except the manual vetting).
If the search returns a planet candidate---passing all of the same cuts as we
apply in the main search (except the manual vetting)---with period and
reference transit time within 6~hours of the injected signal, we count that
injection as recovered.
The detection efficiency of the search is given approximately by the fraction
of recovered injections as a function of the relevant parameters.

@@

\figurename s~\figref{completeness} and~\figref{completeness-mag} show the
fraction of recovered signals as a function of the physical parameters of the
injection and the magnitude of the star in the \kepler\ bandpass as reported
in the Ecliptic Plane Input Catalog
(EPIC\footnote{\url{http://archive.stsci.edu/k2/epic.pdf}}).
As expected, the shallower transits at longer periods are recovered less
robustly and all signals become harder to detect for fainter stars.
It is worth noting that these \figurename s are projections (or
marginalizations) of a higher dimensional measurement of the recovery rate as
a function of all of the input parameters.
For example, this detection efficiency map is conditioned on our assumptions
about the eccentricity distribution of planets and it is marginalized over the
empirical distribution of stellar parameters.
It is possible to relax this assumption and apply different distributions by
re-weighting the simulations used to generate this figure.
Therefore, alongside this \paper, we publish the full list of injection
simulations\footnote{\datareleaseurl} to be used for population inference
(occurrence rate measurements).

@@

\begin{figure}[p]
\begin{center}
\includegraphics{figures/completeness-mag.pdf}
\end{center}
\caption{%
Like \fig{completeness}, the empirically measured detection efficiency of the
search procedure as a function of stellar magnitude as reported by the EPIC.
This never reaches 90~percent because these numbers are marginalized over the
range of physical parameters shown in \fig{completeness}.
Even for the brightest stars, the long period, small transits cannot be
detected.
\figlabel{completeness-mag}}
\end{figure}

\begin{figure}[p]
\begin{center}
\includegraphics{figures/performance.pdf}
\end{center}
\caption{%
\response{%
The 6-hour CDPP \citep{Christiansen:2012} for each light curve in Campaign 1
after subtracting the best fit linear combination of 150 ELCs.
For each star, the precision is plotted as a function of the \kepler\
magnitude reported in the EPIC.
The ``outliers'' in the bottom right corner of the plot are caused by a
bright star within the photometric aperture and the points in the top left
corner of the plot are variable stars where the major trends in the light
curve are not caused by systematic effects, making the ELC model a bad fit.}
\figlabel{performance}}
\end{figure}

@@

The flexible systematics model we employ is a 150-parameter linear combination
of PCA components derived from the full set of 21,703 stellar light curves.
That is, it presumes that the systematics afflicting each star are shared in
some way across other stars \response{while the astrophysical signals are
causally unconnected}.
\response{This assumption means that, while there is no formal guarantee that
the basis contains no astrophysical signals, it is unlikely that the top
components will be contaminated.}
It is our belief---although not a strict assumption of our model---that the
systematics are caused primarily by pointing drifts, or movements of the
pixels in the focal plane relative to the stars.
In principle, if the systematics \emph{are} dominated by pointing issues, the
systematics model could require only three parameters---three Euler
angles---not 150 amplitudes.
However, because (as the pointing drifts) each star sees it's own unique
local patch of flat-field variations, the mapping from pointing drifts to
brightness variations can be extremely non-linear.
Furthermore, because when the pointing is moving fast there is a smearing of
the point-spread function, there are effects keyed to the time derivative of
the Euler angles as well.
The large number (150) of linear coefficients gives the linear model the
freedom to model complex non-linear behavior; we are trading off parsimony
in parameters with the enormous computational advantages of maintaining
linearity (and therefore also convexity).
The computational advantages of the linear model are three-fold:
Convexity obviates searching in parameter space for alternative modes;
linear least-squares optimization can be performed with simple linear algebra;
given Gaussian uncertainties and uninformative priors, marginalizations over
the linear parameters also reduces to pure linear algebra.

>>>>

% Notation for this paper.
\newcommand{\flux}{{\ensuremath{\bvec{f}}}}
\newcommand{\ferr}{{\ensuremath{\sigma_f}}}
\newcommand{\attime}{{\ensuremath{t}}}
\newcommand{\basis}{{\bvec{A}}}
\newcommand{\weights}{{\bvec{w}}}

@@

\newcommand{\nyu}{2}
\newcommand{\caltech}{3}
\newcommand{\cfa}{4}
\newcommand{\mpia}{5}
\newcommand{\cds}{6}
\newcommand{\princeton}{7}
\newcommand{\mpis}{8}
\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\nyu},
    Benjamin~T.~Montet\altaffilmark{\caltech,\cfa},
    David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
    Timothy~D.~Morton\altaffilmark{\princeton},
    Dun~Wang\altaffilmark{\nyu}, \&
    Bernhard~Sch\"olkopf\altaffilmark{\mpis}
}
\altaffiltext{1}         {To whom correspondence should be addressed:
                          \url{danfm@nyu.edu}}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          Department of Physics, New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\caltech}  {Cahill Center for Astronomy and Astrophysics,
                          California Institute of Technology, Pasadena, CA,
                          91125, USA}
\altaffiltext{\cfa}      {Harvard-Smithsonian Center for Astrophysics,
                          Cambridge, MA 02138, USA}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\cds}      {Center for Data Science,
                          New York University,
                          726 Broadway, 7th Floor, New York, NY, 10003, USA}
\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
                          Princeton, NJ, 08544, USA}
\altaffiltext{\mpis}     {Max Planck Institute for Intelligent Systems,
                          Spemannstrasse 38, 72076 T\"ubingen, Germany}

@@

One key realization that is also exploited by the official \kepler\ pipeline
is that the systematic trends caused by pointing shifts and other instrumental
effects are shared---with different signs and weights---by all the stars on
the focal plane.
For a rigorous theoretical analysis of this problem, see Sch\"olkpf
\etal\ (ICML, in press).
To capitalize on this, the \pdc\ component of the \kepler\ pipeline
removes any trends from the light curves that can be fit using a linear
combination of a small number of ``co-trending basis vectors''.
This basis of trends was found by running Principal Component Analysis (PCA)
on a large set of (filtered) light curves and extracting the top few ($\sim
4$) components \citep{Stumpe:2012, Smith:2012}.
Similarly, we ran PCA on the full set of our own generated \KT\ Campaign~1
light curves to determine a basis of representative trends but, unlike \pdc,
we retain and use a larger number of these components ($150$).
For clarity, we will refer to our basis as a set of ``eigen light curves''
(ELCs) and the full set is made available online\footnote{\datareleaseurl}.
The top ten ELCs for Campaign~1 are shown in \Fig{pca}.

@@

Physically, the motivation for our model---and the \pdc\ model---is that every
star on the detector should be affected by the same set of systematic effects.
These are caused by things like pointing jitter, temperature variations, and
other sources of PSF modulation.
Each of these effects will be imprinted in the light curves of many stars with
varying amplitudes and signs as a result of the varying flat field and PSF.
Therefore, while it is hard to write down a physical generative model for the
systematics, building a data-driven model might be possible.
This intuition is also exploited by other methods that model the systematics
using only empirical centroids \citep{Vanderburg:2014, Armstrong:2014,
Aigrain:2015, Crossfield:2015}, but our more flexible model should capture a
wider range of effects, including those related to PSF and temperature.
For example, \Fig{corr} shows the application of our model---with 150
ELCs---to a light curve with no known transit signals and the photometric
precision is excellent.

@@

In our pipeline we simultaneously fit for the transit signal and the trends
using a rigid model for the signal and a relatively flexible model for the
systematic noise.
Specifically, we model the light curve as being generated by linear
combination of 150 ELCs and a ``box'' transit model at a specific period,
phase, and duration.
The mathematical details are given in \app{math}, but in summary, since the
model is linear, we can analytically compute the likelihood
function---conditioned on a specific period, phase, and duration---for the
depth \emph{marginalizing out the parameters of the systematics model}.
The signal-to-noise of this depth measurement can then be used as a quality of
fit metric or candidate selection scalar.
This computation is expensive but, as described in the following \sectionname
s, it is possible to scale the method to a \KT-size dataset.
\response{The bottom panel of \Fig{overfitting} shows the application of this
joint transit--systematics model to the synthetic transit discussed
previously.
When the joint model is used, the correct transit depth is measured---the
transit is not distorted---but the systematics are also well-described by the
model.}

@@

\begin{figure}[p]
\begin{center}
\includegraphics{figures/corr.pdf}
\end{center}
\caption{%
A demonstration of the eigen light curve (ELC) fit to the aperture photometry
for EPIC 201374602.
\emph{Top:} The black points show the aperture photometry and the green line
is the maximum likelihood linear combination of ELCs.
The estimated 6-hour precision of the raw photometry is 264 ppm.
\emph{Bottom:} The points show the residuals of the data away from the ELC
prediction.
The 6-hour precision of this light curve is 31 ppm.
Note that although we show a ``de-trended'' light curve to give a qualitative
understanding of the model, this is not a product of the analysis.
In this search for transits, \emph{the data are only de-trended for the
purpose of visualization}.
\figlabel{corr}}
\end{figure}

\begin{figure}[p]
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/overfitting.pdf}
\end{center}
\caption{%
\response{%
A comparison between de-trending using different numbers of ELCs and a
simultaneous fit of the systematics and transit model.
\emph{(a)} The raw photometry for EPIC 201374602 with a synthetic transit
injected at 65 days.
% In all plots, the photometry is measured in parts-per-thousand (ppt).
\emph{(b)} The black points show the photometry de-trended using a linear
combination of 10 ELCs and the green line shows the true transit model.
In this panel and the next, the maximum likelihood transit depth is computed
following \project{BLS} \citep{Kovacs:2002}.
While some of the systematics are removed by this model, there is still a lot
of residual noise.
\emph{(c)} The same plot as panel \emph{(b)} but using 150 ELCs to de-trend.
This model removes the majority of the systematics but also distorts the
transit and weakens the signal; it reduces the measured transit depth.
\emph{(d)} The final panel shows the results of simultaneously fitting for
the transit and the systematics using 150 ELCs.
The maximum likelihood depth (marginalized over the ELC weights) is computed
as described in \app{math}.
Like panel \emph{(c)}, this model removes most of the systematics but does
not distort the transit or reduce the measured transit depth.
}
\figlabel{overfitting}}
\end{figure}

@@

Specifically, we must evaluate the likelihood function for the light curve
$\flux_n$ of star $n$ given a period \period, reference transit time \phase,
duration \duration, \response{and depth \depth}
\begin{eqnarray}\eqlabel{full-likelihood}
p(\flux_n\,|\,\period,\,\phase,\,\duration,\,\depth) \quad.
\end{eqnarray}
We make the simplifying assumption that each transit enters this quantity
independently.
This is not true; as we change beliefs about each transit, we change beliefs
about the systematics model, which in turn affects the other transits.
However, this simplifying assumption
is approximately satisfied for all but the shortest
periods and leads to a huge computational advantage.
Under this assumption, this likelihood function can be rewritten as
\begin{eqnarray}\eqlabel{indtran}
p(\flux_n\,|\,\period,\,\phase,\,\duration,\,\depth) &=&
\prod_{m=1}^{M(\period,\,\phase)}
    p(\flux_n\,|\,\transittime_m(\period,\,\phase),\,\duration,\,
                    \depth)
\end{eqnarray}
where $\transittime_m(\period,\,\phase)$ is the time of the $m$-th
transit given the period $\period$ and reference time $\phase$, and
\response{$M(\period,\,\phase)$ is the total number of transits in the dataset
for the given \period\ and \phase}.
\Eq{indtran} can be efficiently computed for many periods and phases if we
first compute a set of likelihood functions for single transits on a grid
in $\transittime_l$ and duration $\duration_k$
\begin{eqnarray}\eqlabel{singletransit}
\left \{ p(\flux_n\,|\,\transittime_l,\,\duration_k,\,\depth)
\right\}_{l=1,\,k=1}^{L,\,K} \quad.
\end{eqnarray}
Then, we can use these results as a look-up table\response{---with
nearest-neighbor interpolation---}to approximately evaluate the full
likelihood in \eq{full-likelihood}.

@@

The linear search requires hypothesizing a set of transit signals on a
two-dimensional grid in transit time and duration.
For each point in the grid, we use the model described in \sect{model} to
evaluate \emph{the likelihood function} for the transit depth at that time
and duration.
Since the model is linear and the uncertainties are assumed Gaussian, the
likelihood function for the depth (marginalized over the model of the
systematics) is a Gaussian with analytic amplitude $L$, mean $\bar{\depth}$,
and variance $\delta\bar{\depth}^2$, all derived and given in \app{math}.
In the linear search, we save these three numbers on a
two-dimensional grid of transit times $\transittime_l$ and durations
$\duration_k$.
The transit time grid spans the full length of Campaign~1 with half hour spacing
and we choose to only test three durations: 1.2, 2.4, and 4.8 hours.
\Fig{linear} shows the maximum likelihood transit depth $\bar{\depth}$ as a
function of transit time \transittime\ for the light curve of EPIC 201613023,
a transiting planet candidate with a period of 8.3~days.

@@

\response{%
In the period search step, the table of likelihood functions generated in the
linear search step are used to compute the likelihood of the periodic model
(\eqalt{indtran}) on a three dimensional grid in period \period, reference
time \phase, and duration \duration.
At each point in this grid, the likelihood function for each transit depth is
chosen as the nearest point (without interpolation) calculated in the linear
search.
If the time spacing of the linear search is sufficiently fine, this will give
a good approximation of the correct periodic likelihood.}
For each periodic model, we compute the likelihood of a model where the
transit depth varies between transits and the ``correct'' simpler model where
the transit depth is constant.
The variable depth likelihood is given by the product of amplitudes from the
initial search
\begin{eqnarray}
p_\mathrm{var}(\flux_n\,|\,\period,\,\phase,\,\duration) &=&
\prod_{m=1}^{M(\period,\,\phase)} L_m \quad.
\end{eqnarray}
Since the likelihood function for the depth at each transit time is known and
Gaussian, the likelihood function for the depth under the periodic model can
also be computed analytically; it is a product of Gaussians which itself is a
Gaussian
\begin{eqnarray}
p_\mathrm{const}(\flux_n\,|\,\period,\,\phase,\,\duration) &=&
\prod_{m=1}^{M(\period,\,\phase)}
    \frac{L_m}{\sqrt{2\,\pi\,{\delta\bar{\depth}_m}^2}}\,\exp \left(
        -\frac{[\depth - \bar{\depth}_m]^2}{2\,{\delta\bar{\depth}_m}^2}
    \right)
\end{eqnarray}
where the maximum likelihood depth, for the periodic model, is
\begin{eqnarray}\eqlabel{periodic-depth}
\depth &=& {\sigma_\depth}^2\,\sum_{m=1}^{M(\period,\,\phase)}
    \frac{\bar{\depth}_m}{{\delta\bar{\depth}_m}^2}
\end{eqnarray}
and the uncertainty is given by
\begin{eqnarray}\eqlabel{periodic-depth-uncert}
\frac{1}{{\sigma_\depth}^2} &=& \sum_{m=1}^{M(\period,\,\phase)}
    \frac{1}{{\delta\bar{\depth}_m}^2} \quad.
\end{eqnarray}
Note that this result has been \emph{marginalized} over the parameters of the
systematics model.
Therefore, this estimate of the uncertainty on the depth takes any
uncertainty that we have about the systematics into account.

In general, the variable depth model will \emph{always} get a higher
likelihood because it is more flexible.
Therefore, a formal model comparison is required to compete these two models
against each other on equal footing.
For computational simplicity and speed, we use the Bayesian Information
Criterion (BIC).
The traditional definition of the BIC is
\begin{eqnarray}
-\frac{1}{2}\,\BIC &=&
    \ln p(\flux_n\,|\,\period,\,\phase,\,\duration)
    - \frac{K}{2} \ln N
\end{eqnarray}
where the likelihood function is evaluated at the maximum, $K$ is an estimate
of the model complexity and $N$ is the effective sample size.
To emphasize that $K$ and $N$ are tuning parameters of the method, we
rewrite this equation as
\begin{eqnarray}
-\frac{1}{2}\,\BIC &=&
    \ln p(\flux_n\,|\,\period,\,\phase,\,\duration) -
        \frac{J\,\alpha}{2}
\end{eqnarray}
where $J$ is the number of allowed depths---one for the constant depth model
and the number of transits for the variable depth model---and $\alpha$ is
chosen heuristically.
For the K2 Campaign~1 dataset, we find that $\alpha \sim 1240$ leads to
reliable recovery of injected signals while still being fairly insensitive to
false signals.

@@

To do first-pass vetting for blended EBs among our catalog of
planetary candidates, we test for significant centroid offsets using
the machinery that we have already established for modeling the
systematic trends in the data, inspired by the methods used to vet
\kepler\ candidates \citep{Bryson:2013}.
If any of the candidates have substantial centroid offsets in phase with their
transits, this indicates that the signal is likely caused by a background or
foreground transit of an eclipsing binary and we, therefore, remove it from
the final candidate list.
This is only an initial vetting step and a more complete characterization of
our catalog's reliability is forthcoming (Montet, \etal\ in preparation).

@@

To test the performance and detection efficiency of our method, we conducted a
suite of injection and recovery tests, five per
star for all 21,703 target stars.
For each test, we inject the signal from a realistic planetary system into the
raw aperture photometry of a random target and run the resulting injected
light curve through the full pipeline (except the manual vetting).
If the search returns a planet candidate---passing all of the same cuts as we
apply in the main search (except the manual vetting)---with period and
reference transit time within 6~hours of the injected signal, we count that
injection as necovered.
The detection efficiency of the search is given approximately by the fraction
of recovered injections as a function of the relevant parameters.

@@

\figurename s~\figref{completeness} and~\figref{completeness-mag} show the
fraction of recovered signals as a function of the physical parameters of the
injection, and the magnitude of the star in the \kepler\ bandpass as reported
in the Ecliptic Plane Input Catalog
(EPIC\footnote{\url{http://archive.stsci.edu/k2/epic.pdf}}).
As expected, the shallower transits at longer periods are recovered less
robustly and all signals become harder to detect for fainter stars.
It is worth noting that these \figurename s are projections (or
marginalizations) of a higher dimensional measurement of the recovery rate as
a function of all of the input parameters.
For example, this detection efficiency map is conditioned on our assumptions
about the eccentricity distribution of planets and it is marginalized over the
empirical distribution of stellar parameters.
It is possible to relax this assumption and apply different distributions by
re-weighting the simulations used to generate this figure.
Therefore, alongside this \paper, we publish the full list of injection
simulations\footnote{\datareleaseurl} to be used for population inference
(occurrence rate measurements).

@@

\begin{figure}[p]
\begin{center}
\includegraphics{figures/completeness-mag.pdf}
\end{center}
\caption{%
Like \fig{completeness}, the empirically measured detection efficiency of the
search procedure as a function of stellar magnitude as reported by the
Ecliptic Plane Input Catalog.
This never reaches 90~percent because these numbers are marginalized over the
range of physical parameters shown in \fig{completeness}.
Even for the brightest stars, the long period, small transits cannot be
detected.
\figlabel{completeness-mag}}
\end{figure}

\begin{figure}[p]
\begin{center}
\includegraphics{figures/performance.pdf}
\end{center}
\caption{%
\response{%
The 6-hour CDPP \citep{Christiansen:2012} for each light curve in Campaign 1
after subtracting the best fit linear combination of 150 ELCs.
For each star, the precision is plotted as a function of the \kepler\
magnitude reported in the Ecliptic Plane Input Catalog.
The ``outliers'' in the bottom right corner of the plot are caused by a
bright star within the photometric aperture and the points in the top left
corner of the plot are variable stars where the major trends in the light
curve are not caused by systematic effects, making the ELC model a bad fit.}
\figlabel{performance}}
\end{figure}

@@

The flexible systematics model we employ is a 150-parameter linear combination
of PCA components derived from the full set of 21,703 stellar light curves.
That is, it presumes that the systematics afflicting each star are shared in
some way across other stars \response{while the astrophysical signals are
causally unconnected (Sch\"olkopf \etal\ ICML in press)}.
\response{This assumption means that, while there is no formal guarantee that
the basis contains no astrophysical signals, it is unlikely that the top
components will be contaminated.}
It is our belief---although not a strict assumption of our model---that the
systematics are caused primarily by pointing drifts, or movements of the
pixels in the focal plane relative to the stars.
In principle, if the systematics \emph{are} dominated by pointing issues, the
systematics model could require only three parameters---three Euler
angles---not 150 amplitudes.
However, because (as the pointing drifts) each star sees its own unique
local patch of flat-field variations, the mapping from pointing drifts to
brightness variations can be extremely non-linear.
Furthermore, because when the pointing is moving fast there is a smearing of
the point-spread function, there are effects keyed to the time derivative of
the Euler angles as well.
The large number (150) of linear coefficients gives the linear model the
freedom to model complex non-linear behavior; we are trading off parsimony
in parameters with the enormous computational advantages of maintaining
linearity (and therefore also convexity).
The computational advantages of the linear model are three-fold:
Convexity obviates searching in parameter space for alternative modes;
linear least-squares optimization can be performed with simple linear algebra;
given Gaussian uncertainties and uninformative priors, marginalizations over
the linear parameters also reduces to pure linear algebra.
